Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
car socio

## Caribou socioecology
<!--Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on predicted social (visual and auditory perception), spatial
(habitat type), and temporal (seasonal) scales.--> Caribou are gregarious ungulates
with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
is presumed to be a costly behaviour and as a result, caribou tend to occupy and
re-use craters once they are established and there is considerably less access
to forage than when the landscape is snow-free. Importantly, craters exist on
the landscape at multiple scales: the crater scale (a single crater), the
feeding area scale (multiple craters in close proximity), and the winter range
scale (all craters within an individual’s range) [@Mayor_2009]. The distribution
of forage for caribou is therefore seasonally heterogeneous because the
distribution of craters on the landscape varies meaning that access to
vegetation in winter is highly variable for caribou in winter compared to summer. Caribou therefore have
greater access to forage in snow-free seasons. <!--We partitioned data into two
discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
February 2018) based on caribou socioecology [@Peignier_2019].-->

## Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017, 2018 and 2019.
Adult female caribou were immobilized and fitted with global positioning system
(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
discrete removed all erroneous and outlier GPS fixes following
[@Bjorneraas_2010]. We did not collar all caribou in
the herd; however, the proportion of marked adult females was ~10% of all adult
females and ~5% of all individuals in the herd. We assumed these individuals
were randomly distributed throughout the population.

>>>>

## Caribou socioecology
<!--Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on predicted social (visual and auditory perception), spatial
(habitat type), and temporal (seasonal) scales.--> Caribou are gregarious ungulates
with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
is presumed to be a costly behaviour and as a result, caribou tend to occupy and
re-use craters once they are established. <!-- and there is considerably less access
to forage than when the landscape is snow-free.--> Importantly, craters exist on
the landscape at multiple scales: the crater scale (a single crater), the
feeding area scale (multiple craters in close proximity), and the winter range
scale (all craters within an individual’s range) [@Mayor_2009]. Access to forage is 
seasonally heterogeneous depending on snow cover and, in winter, variable distribution of craters on the 
landscape. <!--We partitioned data into two
discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
February 2018) based on caribou socioecology [@Peignier_2019].-->

## Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017, 2018 and
2019. Adult female caribou were immobilized and fitted with global positioning
system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
collars, 1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
to remove all erroneous and outlier GPS fixes following
[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
proportion of marked adult females was ~10% of all adult females and ~5% of all
individuals in the herd. We assumed these individuals were randomly distributed
throughout the population.
